---
title: "Comparing and Regression current data and Accurate data"
output: html_document
---

```{r setup1, warning=FALSE, include=FALSE}
# library, setup
library(ggplot2)
library(UsingR)
library(car)
library(gridExtra)
par("mar")
par(mar=c(1,1,1,1))
```

```{r setup2, warning=FALSE, include=FALSE}
test = read.csv("feed.csv",header = TRUE)
acc = read.csv("tem_hum_com.csv", header = TRUE)
test1 = test[,3:4]

temperature <- test1[,1]
humidity <- test1[,2]
temperature_com <- acc[,1]
humidity_com <- acc[,2]
```

## View data

### information of current data
```{r str1, warning=FALSE, echo=FALSE}
str(test1)
```

### information of accurate data
```{r str2, warning=FALSE, echo=FALSE}
str(acc)
```

### summarize of current data
```{r summary1, warning=FALSE, echo=FALSE}
summary(test1)
```

### summarize of accurate data
```{r summary2, warning=FALSE, echo=FALSE}
summary(acc)
```


### histogram of current data
```{r histogram1, warning=FALSE, echo=FALSE}
par(mfow=c(1,2))
hist(temperature, col="blue", breaks=100)
hist(humidity, col="blue", breaks=100)

```

### histogram of accurate data
```{r histogram2, warning=FALSE, echo=FALSE}
par(mfow=c(1,2))
hist(temperature_com, col="red", breaks = 100)
hist(humidity_com, col="red", breaks = 100)
par(mfrow=c(1,1))
```

## Correlation with temperature and humidity data
##### Source : http://rstudio-pubs-static.s3.amazonaws.com/189354_277dfb3a83a34a2abaae855b90fcf269.html


### correlation test for current data
```{r correlation1, warning=FALSE, echo=FALSE}
cor.test(temperature, humidity)
```

### correlation test for accurate data
```{r correlation2, warning=FALSE, echo=FALSE}
cor.test(temperature_com, humidity_com)
```

### ggplot for current data
```{r ggplot1, warning=FALSE, echo=FALSE}
ggplot(data = test1, aes(x=temperature, y=humidity))+geom_count()+geom_smooth(method="lm")
```

### ggplot for accurate data
```{r ggplot2, warning=FALSE, echo=FALSE}
ggplot(data = acc, aes(x=temperature_com, y=humidity_com))+geom_count()+geom_smooth(method="lm")
```

### fit current data and draw for linear regression
```{r linear1, warning=FALSE, echo=FALSE}
fit <- lm(temperature~humidity, data = test1)
summary(fit)
```

### fit accurate data and draw for linear regression
```{r linear2, warning=FALSE, echo=FALSE}
fit_com <- lm(temperature_com~humidity_com, data = acc)
summary(fit_com)
```

### graph with current data and linear regression line
```{r linear3, warning=FALSE, echo=FALSE}
plot(temperature~humidity, data=test1)
abline(fit, col="blue")
```


### graph with accurate data and linear regression line
```{r linear4, warning=FALSE, echo=FALSE}
plot(temperature_com~humidity_com, data=acc)
abline(fit_com, col="red")
```

### graph with current data and linear regression line with accurate data
```{r linear5, warning=FALSE, echo=FALSE}
plot(temperature~humidity, data=test1)
abline(fit_com, col="red")
```

### fit current data and draw for 2nd polynomial regression
```{r 2nd poly1, warning=FALSE, echo=FALSE}
fit2 <- lm(temperature~humidity+I(humidity^2), data=test1)
summary(fit2)
```

### fit accurate data and draw for 2nd polynomial regression
```{r 2nd poly2, warning=FALSE, echo=FALSE}
fit2_com <- lm(temperature_com~humidity_com+I(humidity_com^2), data=acc)
summary(fit2_com)
```

### graph with current data and 2nd polynomial regression line
```{r 2nd poly3, warning=FALSE, echo=FALSE}
plot(temperature~humidity, data=test1)
lines(test1$humidity, fitted(fit2), col="blue")
```

### graph with accurate data and 2nd polynomial regression line
```{r 2nd poly4, warning=FALSE, echo=FALSE}
plot(temperature_com~humidity_com, data=acc)
lines(acc$humidity, fitted(fit2_com), col="red")
```

### graph with current data and 2nd polynomial regression line with accurate data
```{r 2nd poly5, warning=FALSE, echo=FALSE}
plot(temperature~humidity, data=test1)
lines(acc$humidity, fitted(fit2_com), col="red")
```

### fit current data and draw for 3rd polynomial regression
```{r 3rd poly1, warning=FALSE, echo=FALSE}
fit3 <- lm(temperature~humidity + I(humidity^2) + I(humidity^3), data=test1)
summary(fit3)
```

### fit accurate data and draw for 3rd polynomial regression
```{r 3rd poly2, warning=FALSE, echo=FALSE}
fit3_com <- lm(temperature_com~humidity_com + I(humidity_com^2) + I(humidity_com^3), data=acc)
summary(fit3_com)
```

### graph with current data and 3rd polynomial regression line
```{r 3rd poly3, warning=FALSE, echo=FALSE}
plot(temperature~humidity, data=test1)
lines(test1$humidity, fitted(fit3), col="blue")
```

### graph with accurate data and 3rd polynomial regression line(It's close same as linear regression line)
```{r 3rd poly4, warning=FALSE, echo=FALSE}
plot(temperature_com~humidity_com, data=acc)
lines(acc$humidity, fitted(fit3_com), col="red")
```

### graph with current data and 3rd polynomial regression line with accurate data
```{r 3rd poly5, warning=FALSE, echo=FALSE}
plot(temperature~humidity, data=test1)
lines(acc$humidity, fitted(fit3_com), col="red")
```

### made scatterplot with current data
```{r scatter1, warning=FALSE, echo=FALSE}
scatterplot(temperature~humidity, data=test1, pch=19,
            spread=FALSE, smoother.args=list(lty=2),
            main="current data",
            xlab="Temperature(Celsius)", ylab="Humidity(mm)")
```

### made scatterplot with accurate data
```{r scatter2, warning=FALSE, echo=FALSE}
scatterplot(temperature_com~humidity_com, data=acc, pch=19,
            spread=FALSE, smoother.args=list(lty=2),
            main="Compare data",
            xlab="Temperature(Celsius)", ylab="Humidity(mm)")
```