---
title: "Do regression and correlation using current data and processing using accurate data"
output: html_document
---

```{r setup1, warning=FALSE, include=FALSE}
# library, setup
library(ggplot2)
library(UsingR)
library(car)
library(gridExtra)
par("mar")
par(mar=c(1,1,1,1))
```

```{r setup2, warning=FALSE, include=FALSE}
test = read.csv("feeds.csv",header = TRUE)
acc = read.csv("tem_hum_com.csv", header = TRUE)
test <- na.omit(test)

test[,4] <- test[,4] * 0.01
data = test[,3:4]
time = test[,1]
data$time = time
colnames(data) = c("temperature", "humidity", "time")
colnames(acc) = c("temperature_com", "humidity_com")
```

## View data

### information of current data
```{r str1, warning=FALSE, echo=FALSE}
str(data)
```

### information of accurate data
```{r str2, warning=FALSE, echo=FALSE}
str(acc)
```

### summarize of current data
```{r summary1, warning=FALSE, echo=FALSE}
summary(data)
```

### summarize of accurate data
```{r summary2, warning=FALSE, echo=FALSE}
summary(acc)
```

### histogram of current data
```{r histogram1, warning=FALSE, echo=FALSE}
current = data[seq(nrow(data), nrow(data)-45),]
current = current[c(order(current$time)),]

p = ggplot(data = current, aes(x=time, y=temperature))+geom_point()
p1 = ggplot(data = current, aes(x=time, y=humidity))+geom_point()
grid.arrange(p,p1,ncol=2)
```

## Correlation with temperature and humidity data
##### Source : http://rstudio-pubs-static.s3.amazonaws.com/189354_277dfb3a83a34a2abaae855b90fcf269.html


### correlation test for current data
```{r correlation1, warning=FALSE, echo=FALSE}
cor.test(data$temperature, data$humidity)
```

### correlation test for accurate data
```{r correlation2, warning=FALSE, echo=FALSE}
cor.test(acc$temperature_com, acc$humidity_com)
```

### ggplot for current data
```{r ggplot1, warning=FALSE, echo=FALSE}
ggplot(data = data, aes(x=temperature, y=humidity))+geom_count()+geom_smooth(method="lm")
```

### ggplot for accurate data
```{r ggplot2, warning=FALSE, echo=FALSE}
ggplot(data = acc, aes(x=temperature_com, y=humidity_com))+geom_count()+geom_smooth(method="lm")
```

### fit current data and draw for linear regression
```{r linear1, warning=FALSE, echo=FALSE}
fit <- lm(humidity~temperature, data = data)
summary(fit)
```

### fit accurate data and draw for linear regression
```{r linear2, warning=FALSE, echo=FALSE}
fit_com <- lm(humidity_com~temperature_com, data = acc)
summary(fit_com)
```

### graph with current data and linear regression line
```{r linear3, warning=FALSE, echo=FALSE}
plot(humidity~temperature, data=data)
abline(fit, col="blue")
```

### graph with accurate data and linear regression line
```{r linear4, warning=FALSE, echo=FALSE}
plot(humidity_com~temperature_com, data=acc)
abline(fit_com, col="red")
```

### graph with current data and linear regression line with accurate data
```{r linear5, warning=FALSE, echo=FALSE}
plot(humidity~temperature, data=data)
abline(fit_com, col="red")
```

### fit current data and draw for 2nd polynomial regression
```{r 2nd poly1, warning=FALSE, echo=FALSE}
fit2 <- lm(humidity~temperature+I(temperature^2), data=data)
summary(fit2)
```

### fit accurate data and draw for 2nd polynomial regression
```{r 2nd poly2, warning=FALSE, echo=FALSE}
fit2_com <- lm(humidity_com~temperature_com+I(temperature_com^2), data=acc)
summary(fit2_com)
```

### graph with current data and 2nd polynomial regression line
```{r 2nd poly3, warning=FALSE, echo=FALSE}
plot(humidity~temperature, data=data)
lines(data$temperature, fitted(fit2), col="blue")
```

### graph with accurate data and 2nd polynomial regression line
```{r 2nd poly4, warning=FALSE, echo=FALSE}
plot(humidity_com~temperature_com, data=acc)
lines(acc$temperature_com, fitted(fit2_com), col="red")
```

### graph with current data and 2nd polynomial regression line with accurate data
```{r 2nd poly5, warning=FALSE, echo=FALSE}
plot(humidity~temperature, data=data)
lines(acc$temperature_com, fitted(fit2_com), col="red")
```

### fit current data and draw for 3rd polynomial regression
```{r 3rd poly1, warning=FALSE, echo=FALSE}
fit3 <- lm(humidity~temperature + I(temperature^2) + I(temperature^3), data=data)
summary(fit3)
```

### fit accurate data and draw for 3rd polynomial regression
```{r 3rd poly2, warning=FALSE, echo=FALSE}
fit3_com <- lm(humidity_com~temperature_com + I(temperature_com^2) + I(temperature_com^3), data=acc)
summary(fit3_com)
```

### graph with current data and 3rd polynomial regression line
```{r 3rd poly3, warning=FALSE, echo=FALSE}
plot(humidity~temperature, data=data)
lines(data$temperature, fitted(fit3), col="blue")
```

### graph with accurate data and 3rd polynomial regression line
```{r 3rd poly4, warning=FALSE, echo=FALSE}
plot(humidity_com~temperature_com, data=acc)
lines(acc$temperature_com, fitted(fit3_com), col="red")
```

### graph with current data and 3rd polynomial regression line with accurate data
```{r 3rd poly5, warning=FALSE, echo=FALSE}
plot(humidity~temperature, data=data)
lines(acc$temperature_com, fitted(fit3_com), col="red")
```

### made scatterplot with current data
```{r scatter1, warning=FALSE, echo=FALSE}
scatterplot(temperature~humidity, data=data, pch=19,
            spread=FALSE, smoother.args=list(lty=2),
            main="current data",
            xlab="Temperature(Celsius)", ylab="Humidity(%)")
```

### made scatterplot with accurate data
```{r scatter2, warning=FALSE, echo=FALSE}
scatterplot(temperature_com~humidity_com, data=acc, pch=19,
            spread=FALSE, smoother.args=list(lty=2),
            main="Compare data",
            xlab="Temperature(Celsius)", ylab="Humidity(%)")
```